Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-02-28 src/article.tex
Christina revisions to abstract

  \paragraph*{Background:} Assembly of short read sequencing data can result in
  a fragmented series of contigs. Therefore a common step in a genome project
  is to join neighbouring sequence regions together and fill gaps in the
  assembly using additional sequence. This scaffolding step, however, is
  non-trivial and requires manually editing large blocks of nucleotide
  sequence. Joining sequence contigs together also hides the source of each
  region in the final genome sequence. Taken together, these considerations may
  make reproducing or editing an existing genome build difficult.

@@

  \paragraph*{Results:} This software allows a genome build to be defined in
  terms of the constituent contigs using a relatively simple to write and edit
  scaffold file syntax. This syntax further allows  unknown regions to be
  defined, and inserts to be added to the scaffold to fill gaps. Defining the
  genome construction in a file makes the scaffolding process reproducible and
  easier to edit and compare than fasta sequence.

  \paragraph*{Conclusions:} Scaffolder is easy to use genome scaffolding
  software. This tool promotes reproducibility and continuous development in a
  genome project. Scaffolder can be found at \scaffolder.

>>>>

  \paragraph*{Background:} Assembly of short read sequencing data can result in
  a fragmented series of sequences. Therefore a common step in a genome project
  is to join neighbouring sequence regions together and fill gaps in the
  assembly using additional sequence. This scaffolding step, however, is
  non-trivial and requires manually editing large blocks of nucleotide
  sequence. Joining sequence contigs together also hides the source of each
  region in the final genome sequence. Taken together, these considerations may
  make reproducing or editing an existing genome build difficult.

@@

  \paragraph*{Results:} This software allows a genome build to be defined in
  terms of the constituent contigs using a relatively simple format to write
  and edit scaffold file syntax. This syntax further allows  unknown regions to
  be defined, and inserts to be added to the scaffold to fill gaps. Defining
  the genome construction in a file makes the scaffolding process reproducible
  and easier to edit and compare than fasta sequence.

  \paragraph*{Conclusions:} Scaffolder is easy-to-use genome scaffolding
  software. This tool promotes reproducibility and continuous development in a
  genome project. Scaffolder can be found at \scaffolder.
